Alternative Methods for Retaining Explicit and Finding Implicit Sharing in Embedded DSLs

### 2023-04-20 paper/paper.tex
fixed typography issue after addChains example

\vspace{-1cm}
\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figs/hashconscmp.png}
  \caption{Number of calls to \mintinline{haskell}{hashcons} plotted against the
    number of \mintinline{haskell}{add} operations performed.
    Hash-consing is performed without explicit sharing and is clearly exponential,
    Triecons (without explicit sharing) and Hashcons Explicit (with explicit
    sharing) overlap and are both linear
  } \label{fig:hashcons}
\end{figure}
As shown in Fig.~\ref{fig:hashcons}, this code will perform approximately
$2^{n+1}$ \mintinline{haskell}{hashcons} operations, where $n$ is the number of \mintinline{haskell}{add}s.

>>>>

% \vspace{-1cm}
\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figs/hashconscmp.png}
  \caption{Number of calls to \mintinline{haskell}{hashcons} plotted against the
    number of \mintinline{haskell}{add} operations performed.
    Hash-consing is performed without explicit sharing and is clearly exponential,
    Triecons (without explicit sharing) and Hashcons Explicit (with explicit
    sharing) overlap and are both linear
  } \label{fig:hashcons}
\end{figure}

As shown in Fig.~\ref{fig:hashcons}, this code will perform approximately
$2^{n+1}$ \mintinline{haskell}{hashcons} operations, where $n$ is the number of \mintinline{haskell}{add}s.
